### 2025-02-09 data-visualization.qmd
20250209 - fix figure labels

A density plot of fantasy points with a histogram and rug plot is depicted in @fig-histogramDensity.

```{r}
#| label: fig-histogramDensity
#| fig-cap: "Density Plot with Histogram and Rug Plot."
#| fig-alt: "Density Plot with Histogram and Rug Plot."

>>>>

A density plot of fantasy points with a histogram and rug plot is depicted in @fig-densityHistogram.

```{r}
#| label: fig-densityHistogram
#| fig-cap: "Density Plot with Histogram and Rug Plot."
#| fig-alt: "Density Plot with Histogram and Rug Plot."
